\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-25 doc/USER_MANUAL/manual_SPECFEM3D.tex
added references to our domain decomposition and weak scaling papers

\item [Numerical simulations in general] ~\\
Forward simulations are described in detail in \cite{TrKoLi08,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,KoGoErMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99} or \cite{KoVi98}. Additional aspects dealing with adjoint simulations are described in
\cite{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10}.

@@

\caption{Example of a mesh partitioning onto four cores. Each single core partition is colored differently. The executable \texttt{xdecompose\_mesh\_SCOTCH} can equally distribute the mesh on any arbitrary number of cores.}

>>>>

\item [Numerical simulations in general] ~\\
Forward simulations are described in detail in \cite{TrKoLi08,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,KoGoErMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99} or \cite{KoVi98}. Additional aspects dealing with adjoint simulations are described in
\cite{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10}.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores in shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,KoGoErMi10,Kom11}.

@@

\caption{Example of a mesh partitioning onto four cores. Each single core partition is colored differently. The executable \texttt{xdecompose\_mesh\_SCOTCH} can equally distribute the mesh on any arbitrary number of cores.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores in shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,KoGoErMi10,Kom11}.}
